---
title: "Fishery Advice - Celtic Seas"
author: "Prepared by: Scott I. Large"
date: "31 March 2016"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 6.5, fig.height = 4.5, fig.path = '')
# devtools::install_github("ICES-dk/rICES", force = FALSE)
# devtools::install_github("hadley/readxl", force = FALSE)
library(rICES)
library(readxl)
library(dplyr)
library(RColorBrewer)
library(knitr)
library(XML)
library(stringr)
library(reshape2)
library(ggplot2)
#
plotDir = "output/"
options(scipen = 5)
#

```

```{r getDat, include = FALSE, cache = TRUE}
catchURL <- "http://ices.dk/marine-data/Documents/CatchStats/OfficialNominalCatches.zip"
effortURL <- "http://stecf.jrc.ec.europa.eu/documents/43805/870977/2014_STECF+14-20+-+Fishing+Effort+Regimes+data+tables.zip"
spURL <- "ftp://ftp.fao.org/FI/STAT/DATA/ASFIS_sp.zip"
# 
tmpFileCatch <- tempfile(fileext = ".zip")
tmpFileEffort <- tempfile(fileext = ".zip")
tmpFileSp <- tempfile(fileext = ".zip")
# 
download.file(catchURL, destfile = tmpFileCatch, mode = "wb", quiet = T)
download.file(effortURL, destfile = tmpFileEffort, mode = "wb", quiet = T)
download.file(spURL, destfile = tmpFileSp, mode = "wb", quiet = T)
# 
#```

#```{r loadDat, include = FALSE}
catchDat <- read.csv(unz(tmpFileCatch,
                         "ICESCatchDataset2006-2014.csv"),
                     stringsAsFactors = F, header = T, fill = TRUE)
# 
# 
effortDat <- read_excel(unzip(tmpFileEffort, 
                              files = "Electronic_appendices/Effort_trends_by_country.xlsx"),
                        sheet = "kWdays at sea")
# 
stecfCatchDat <- read_excel(unzip(tmpFileEffort, 
                                  files = "Electronic_appendices/Landings_Discards_Discard-rates.xlsx"),
                            sheet = "Land_Disc_Disc-rate_by_Country")
# 
spList <- read.table(unz(tmpFileSp,
                         "ASFIS_sp_Feb_2015.txt"),
                     header = TRUE,
                     fill = TRUE,
                     stringsAsFactors = FALSE)
# 
# FAO codes and ICES stock codes 
speciesID <- read.csv("~/rCode/Data/ICESspeciesID_v1.csv",
                      stringsAsFactors = FALSE)
# 
# Fishery guilds by ICES stock code
fisheryGuild <- read.csv("~/git/ices-dk/rStockOverview/fisheryGuild.csv",
                         stringsAsFactors = FALSE)
# 
fisheryGuild$speciesID <- toupper(gsub( "-.*$", "", fisheryGuild$Stock.code))
# 
fisheryGuild <- fisheryGuild %>%
  inner_join(speciesID, c("speciesID" = "oldCode")) 
# 
ecoAreaCatch <- toupper(c("27.7.a",
                          "27.7.b", 
                          "27.7.c.2", 
                          "27.7.e", 
                          "27.7.f", 
                          "27.7.g", 
                          "27.7.h",
                          "27.7.j.2", 
                          "27.7.k.2", 
                          "27.6.a",
                          "27.6.b.NK",
                          "27.6.b.2"))
# 
# https://datacollection.jrc.ec.europa.eu/c/document_library/get_file?uuid=62841ee4-dbbd-4628-a7a7-5036ce5d415b&groupId=10213
ecoAreaEffort <- c("6 EU", "3C", "7BCEFGHJK") # Looks wrong, but 3c is STEFC for 7a
# 
guildList <- 
  catchDat %>%
  Filter(f = function(x)!all(is.na(x))) %>%
  filter(Area %in% ecoAreaCatch) %>%
  melt(id.vars = c("Species", "Area", "Units", "Country"),
                   variable.name = "YEAR",
                   value.name = "VALUE") %>%
  mutate(YEAR = as.numeric(gsub("X", "", YEAR))) %>%
  group_by(Species) %>%
  mutate(totalCatch = sum(VALUE, na.rm = TRUE)) %>%
  inner_join(spList, c("Species" = "X3A_CODE")) %>%
  full_join(fisheryGuild, c("Species" = "newCode")) %>%
  select(Species, totalCatch, Scientific_name, English_name, Family, Fisheries.Guild) %>%
  ungroup() %>%
  arrange(-totalCatch) %>%
  filter(is.na(Fisheries.Guild) &
         totalCatch > 0) %>%
  distinct(Scientific_name)
# 
# write.csv(guildList, file = "~/git/ices-dk/FisheriesAdvice/keys-lists/CS_spGuildList.csv",
#           row.names = FALSE)
```

```{r catchDat, include = FALSE}
catchDat <-
  catchDat %>%
  Filter(f = function(x)!all(is.na(x))) %>%
  filter(Area %in% ecoAreaCatch) %>%
  melt(id.vars = c("Species", "Area", "Units", "Country"),
                   variable.name = "YEAR",
                   value.name = "VALUE") %>%
  mutate(YEAR = as.numeric(gsub("X", "", YEAR)))
#
catchCountry <- catchDat %>%
  group_by(YEAR, Country) %>%
  dplyr::summarize(countryCatch = sum(VALUE)) # %>% # Total annual catch
# Convert country codes to proper names
#
```

```{r figure1, echo = FALSE, include = TRUE, fig.cap= "Figure 1. Landings (tonnes) by nation within the Celtic Seas ecoregion (ICES areas: 6a, 6b.2, 6b.NK, 7a, 7b, 7c.2, 7e, 7f, 7g, 7h, 7j.2, 7k.2), as reported to ICES."}
# 
catchPlot <- catchCountry %>%
  group_by(Country) %>%
  dplyr::summarize(countryTotal = sum(countryCatch)) %>% # Overall catch to order plot
  arrange(-countryTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(countryTotal))) %>% 
  inner_join(catchCountry, c("Country" = "Country")) %>%
  dplyr::mutate(Country = replace(Country, RANK > 9, "OTHER")) %>%
  group_by(YEAR, Country) %>%
  dplyr::mutate(countryCatch = sum(countryCatch)) %>%
  distinct(YEAR, Country)
# 
catchPlot$Country <- factor(catchPlot$Country, levels = rev(unique(catchPlot$Country)))
myColors <- c("grey40", brewer.pal(length(unique(catchPlot$Country)) - 1, "Spectral"))
names(myColors) <- levels(catchPlot$Country)
#
ggplot(catchPlot, aes(x = YEAR, y = countryCatch)) +
  geom_area(aes(fill = Country, color = Country), alpha = .8, position = "stack") +
  scale_fill_manual(values = myColors) +
  scale_color_manual(values = myColors) +
  labs(x = "Year",
       y = "Landings (tonnes)",
       fill = "Country",
       color = "Country") +
  theme_bw() 
  # ggsave(filename = paste0(plotDir, "CS_FisheryOverview-figure1.png"), width = 6.5,
  #        height = 4.5)
# 
```
### Figure 1 corrections
* Country names and colors should be consistent between Figure 1 and 2. Need to make a look-up table between STECF and ICES country codes
* Merge UK with Scotland (Northern Ireland, Jersey, etc.)
* Explore pre-2006 up to 1990
** Not exactly straight-forward to add this info
* Spain may be missing? Double check



```{r effortDat, include = FALSE}
effortDat <-
# tt <-
  effortDat %>%
  Filter(f = function(x)!all(is.na(x))) %>%
  filter(reg_area_cod %in% ecoAreaEffort) %>%
  melt(id.vars = c("annex", "reg_area_cod", "reg_gear_cod", "Specon_calc", "country", "vessel_length"), 
       variable.name = "YEAR",
       value.name = "VALUE") %>%
  mutate(YEAR = as.numeric(levels(YEAR))[YEAR])
#
effortCountry <- effortDat %>%
  group_by(YEAR, country) %>%
  dplyr::summarize(countryEffort = sum(VALUE, na.rm = T)) # %>% # Total annual catch
# Convert country codes to proper names

```


```{r figure2, echo = FALSE, include = TRUE, fig.cap= "Figure 2. Effort (kW days at sea) by nation within the Celtic Seas ecoregion (6 EU and 7a, 7b, 7c, 7e, 7f, 7g, 7h, 7j, 7k), as reported to STECF."}
effortPlot <- effortCountry %>%
  group_by(country) %>%
  dplyr::summarize(countryTotal = sum(countryEffort)) %>% # Overall catch to order plot
  arrange(-countryTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(countryTotal))) %>% 
  inner_join(effortCountry, c("country" = "country")) %>%
  dplyr::mutate(country = replace(country, RANK > 9, "OTHER"))%>%
  group_by(YEAR, country) %>%
  dplyr::mutate(countryEffort = sum(countryEffort)) %>%
  distinct(YEAR, country)
# 
effortPlot$country <- factor(effortPlot$country, levels = rev(unique(effortPlot$country)))
myColors <- c("grey40", brewer.pal(length(unique(effortPlot$country)) - 1, "Spectral"))
names(myColors) <- levels(effortPlot$country)
#
ggplot(effortPlot, aes(x = YEAR, y = countryEffort)) +
  geom_area(aes(fill = country, color = country), alpha = .8, position = "stack") +
  # scale_x_continuous(limits = range(effortPlot$YEAR), breaks = seq(from = min(effortPlot$YEAR),
  #                                                                  to = max(effortPlot$YEAR, 
  #                                                                      by = .5))) +
  scale_fill_manual(values = myColors) +
  scale_color_manual(values = myColors) +
  labs(x = "Year",
       y = "Effort (kW days at sea)",
       fill = "Country",
       color = "Country") +
  theme_bw() 
  # ggsave(filename = paste0(plotDir, "CS_FisheryOverview-figure2.png"), width = 6.5,
  #        height = 4.5)
```

## Figure 2 corrections
* (see figure 1: Country names and colors should be consistent between Figure 1 and 2. Need to make a look-up table between STECF and ICES country codes)
* [STECF Reference Metadata](https://datacollection.jrc.ec.europa.eu/c/document_library/get_file?uuid=62841ee4-dbbd-4628-a7a7-5036ce5d415b&groupId=10213) claims that 3c == ICES subarea 7a. Double check
* Check the effort data years... might be an ordinal/nominal issue
* Explore the RDB... should have access


```{r guildDat, include = FALSE}
guildDat <-
  catchDat %>%
  inner_join(spList, c("Species" = "X3A_CODE")) %>%
  full_join(fisheryGuild, c("Species" = "newCode")) 
#
guildCatch <- 
  guildDat %>%
  dplyr::mutate(Fisheries.Guild = ifelse(is.na(Fisheries.Guild), "not defined", Fisheries.Guild)) %>%
  group_by(YEAR, Fisheries.Guild) %>%
  dplyr::summarize(guildCatch = sum(VALUE, na.rm = TRUE)) %>% 
  filter(!is.na(YEAR))
#
```

```{r figure3, echo = FALSE, include = TRUE, fig.cap= "Figure 3. Catch (tonnes) by fishery guild within the Celtic Seas ecoregion(6a, 6b.2, 6b.NK, 7a, 7b, 7c.2, 7e, 7f, 7g, 7h, 7j.2, 7k.2)"}
guildPlot <- guildCatch %>%
  group_by(Fisheries.Guild) %>%
  dplyr::summarize(guildTotal = sum(guildCatch, na.rm = TRUE)) %>% # Overall catch to order plot
  arrange(-guildTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(guildTotal))) %>% 
  inner_join(guildCatch, c("Fisheries.Guild" = "Fisheries.Guild")) %>%
  dplyr::mutate(Fisheries.Guild = replace(Fisheries.Guild, RANK > 9, "OTHER")) %>%
  group_by(YEAR, Fisheries.Guild) %>%
  dplyr::mutate(guildCatch = sum(guildCatch)) %>%
  distinct(YEAR, Fisheries.Guild)
# 
guildPlot$Fisheries.Guild <- factor(guildPlot$Fisheries.Guild, levels = rev(unique(guildPlot$Fisheries.Guild)))
myColors <- c("grey40", brewer.pal(length(unique(guildPlot$Fisheries.Guild)) - 1, "Spectral"))
names(myColors) <- levels(guildPlot$Fisheries.Guild)
#
ggplot(guildPlot, aes(x = YEAR, y = guildCatch)) +
  geom_area(aes(fill = Fisheries.Guild, color = Fisheries.Guild), alpha = .8, position = "stack") +
  scale_fill_manual(values = myColors) +
  scale_color_manual(values = myColors) +
  labs(x = "Year",
       y = "Nominal Catch (tonnes)",
       fill = "Fishery guild",
       color = "Fishery guild") +
  theme_bw() 
  # ggsave(filename = paste0(plotDir, "CS_FisheryOverview-figure3.png"), width = 6.5,
  #        height = 4.5)
```
## Figure 3 corrections
* define "not defined" fishery guilds.




```{r speciesCatch, include = FALSE}
spDat <-
  catchDat %>%
  inner_join(spList, c("Species" = "X3A_CODE")) 
#
spCatch <- 
  spDat %>%
  dplyr::mutate(English_name = ifelse(is.na(English_name), "not defined", English_name))

```

```{r  figure4, echo = FALSE, include = TRUE, fig.cap= "Figure 4. Landings (tonnes) reported to ICES for the 10 species with the greatest gross tonneage within the Celtic Seas ecoregion (6a, 6b.2, 6b.NK, 7a, 7b, 7c.2, 7e, 7f, 7g, 7h, 7j.2, 7k.2)"}
# 
spPlot <- spCatch %>%
  group_by(Species) %>%
  dplyr::summarize(spTotal = sum(VALUE, na.rm = TRUE)) %>% # Overall catch to order plot
  arrange(-spTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(spTotal))) %>% 
  inner_join(spCatch, c("Species" = "Species")) %>%
  dplyr::mutate(Species = replace(Species, RANK > 9, "OTHER"),
                English_name = replace(English_name, RANK > 9, "OTHER")) %>%
  group_by(YEAR, Species, English_name) %>%
  dplyr::mutate(spCatch = sum(VALUE, na.rm = TRUE)) %>%
  distinct(YEAR, Species)
# 
spPlot$English_name <- factor(spPlot$English_name, levels = rev(unique(spPlot$English_name)))
myColors <- c("grey40", brewer.pal(length(unique(spPlot$English_name)) - 1, "Spectral"))
names(myColors) <- levels(spPlot$English_name)
#
ggplot(spPlot, aes(x = YEAR, y = spCatch)) +
  geom_area(aes(fill = English_name, color = English_name), alpha = .8, position = "stack") +
  scale_fill_manual(values = myColors) +
  scale_color_manual(values = myColors) +
  labs(x = "Year",
       y = "Nominal Catch (tonnes)",
       fill = "Common name",
       color = "Common name") +
  theme_bw() 
  # ggsave(filename = paste0(plotDir, "CS_FisheryOverview-figure4.png"), width = 6.5,
  #        height = 4.5)
```
## Figure 4 corrections
* Remove "nei" and "(=Poutassou)" type additions to the FAO species name list


```{r gearEffort, include = FALSE}
stecfCatchDat <-
# tt <-
  stecfCatchDat %>%
  # Filter(f = function(x)!all(is.na(x))) %>%
  filter(reg_area %in% ecoAreaEffort) %>%
  melt(id.vars = c("annex", "reg_area", "country", "reg_gear", "specon", "species"), 
       variable.name = "YEAR",
       value.name = "VALUE") %>%
  mutate(METRIC = as.character(gsub(".*\\s", "", YEAR)),
         YEAR = as.numeric(gsub("\\s.+$", "", YEAR))) %>%
  filter(METRIC == "L")
#
catchGear <- stecfCatchDat %>%
  group_by(YEAR, reg_gear) %>%
  dplyr::summarize(gearEffort = sum(VALUE, na.rm = T)) # %>% # Total annual catch
# Convert country codes to proper names


```

```{r figure5, echo = FALSE, include = TRUE, fig.cap= "Figure 5.  Catch (tonnes) by gear reported to STECF within the Celtic Seas ecoregion (6 EU and 7a, 7b, 7c, 7e, 7f, 7g, 7h, 7j, 7k)"}


```
## Figure 5 corrections
* Find where this data is in STECF data...
* Metier overviews


## Table 1 will be an annex
* Add Fpa and Bpa as additional columns.

## Table will be number of stocks above and below reference points total and then divided into fishery guilds




## Figure YY
* No pair trawl
* Demersal trawl

## Figure 6 (split into 2)
* yellow should be red
* red should be grey
* Should we use catch? 
* Should we repeat Fmsy with Fpa? - no
* Use landings for the time being

## Pie graph should be a table as a summary beneath the stock status (tick mark table) 

## Figure 7
* Change the colors (red, green and grey). Yellow should be red
* Fishery guild not trophic guild
* Absolute bar graphs instead of log
* For the time being use landings

[Celtic Seas Fishery Advice](https://community.ices.dk/Advice/Advice2016/CelticSea/_layouts/15/WopiFrame.aspx?sourcedoc=/Advice/Advice2016/CelticSea/Draft_advice/CelticSeasEcoregion_FisheriesOverviews.docx&action=default)



For questions, please email <A HREF="mailto:scott.large@ices.dk?subject=Nordic Council plots">scott.large@ices.dk</A>.

<!-- ```{r guildlist, echo=FALSE, include=TRUE} -->
<!-- # -->
<!-- guildList <- read.csv("~/git/ices-dk/rStockOverview/fisheryGuild.csv") -->
<!-- # -->
<!-- guildList <- guildList %>% -->
<!--   rename(Stock = Stock.code, -->
<!--          GUILD = Fisheries.Guild) %>% -->
<!--   filter(GUILD %in% c("pelagic", "benthic", "demersal")) %>% -->
<!--   mutate(Stock = tolower(Stock), -->
<!--          Stock = gsub("[[:space:]]", "", Stock)) -->
<!-- # -->

<!-- overTable <- guildList %>% -->
<!--   inner_join(stockTable, c("Stock" = "STOCKID")) %>% -->
<!--   rename(ECOREGION = EcoRegion) %>% -->
<!--   distinct(ECOREGION, GUILD, Stock) %>% -->
<!--   select(ECOREGION, GUILD, Stock, FMSY, MSYBtrigger) %>% -->
<!--   filter(ECOREGION %in% c("North Sea", "Iceland and East Greenland", -->
<!--                           "Widely distributed and migratory stocks", -->
<!--                           "Baltic Sea", "Faroe Plateau Ecosystem", -->
<!--                           "Barents Sea and Norwegian Sea")) %>% -->
<!--   filter(!is.na(FMSY) | !is.na(MSYBtrigger)) %>% -->
<!--   arrange(ECOREGION, GUILD) -->
<!-- # -->
<!-- knitr::kable(overTable, format="markdown") -->
<!-- ``` -->


<!-- ```{r stocktable, echo = FALSE} -->
<!-- # -->
<!-- df <- guildList %>% -->
<!--   inner_join(stockTable, c("Stock" = "STOCKID")) %>% -->
<!--   rename(ECOREGION = EcoRegion) %>% -->
<!--   filter(SpeciesName != "Psetta maxima (historic name)" & -->
<!--            Stock %in% unique(guildList$Stock) & -->
<!--            ECOREGION %in% c("North Sea", "Iceland and East Greenland", -->
<!--                           "Widely distributed and migratory stocks", -->
<!--                           "Baltic Sea", "Faroe Plateau Ecosystem", -->
<!--                           "Barents Sea and Norwegian Sea")) %>% -->
<!--   mutate(fishingPressureDescription = gsub("Fishing Pressure: " , "", fishingPressureDescription), -->
<!--          fishingPressureDescription = gsub("Fishing pressure: " , "", fishingPressureDescription), -->
<!--          stockSizeDescription = ifelse(stockSizeDescription == "NA", "Stock Size: Relative", stockSizeDescription), -->
<!--          FmsyDescription = "FMSY", -->
<!--          stockSizeDescription = gsub("Stock Size: ", "", stockSizeDescription)) %>% -->
<!--   filter(stockSizeDescription != "B/BMSY" | -->
<!--            fishingPressureDescription != "F/FMSY") %>% -->
<!--   group_by(Stock) %>% -->
<!--   mutate(F_FMSY = F / FMSY, -->
<!--          SSB_MSYBtrigger = SSB / MSYBtrigger) %>% -->
<!--   melt(id.vars = c("AssessmentYear",  "ECOREGION", "GUILD","Stock", "Year"), -->
<!--        measure.vars = c("F_FMSY", "SSB_MSYBtrigger"), -->
<!--        variable.name = "METRIC", -->
<!--        value.name = "VALUE") %>% -->
<!--   rename(STOCKID = Stock, -->
<!--          YEAR = Year, -->
<!--          stockValue = VALUE) %>% -->
<!--   filter(!is.na(stockValue)) %>% # remove NA VALUE -->
<!--   group_by(ECOREGION, GUILD, METRIC, YEAR) %>% -->
<!--   mutate(ecoGuildMean = mean(stockValue)) %>% -->
<!--   group_by(ECOREGION, METRIC, YEAR) %>% -->
<!--   mutate(ecoValue = mean(stockValue)) %>% -->
<!--   group_by(METRIC, GUILD, YEAR) %>% -->
<!--   mutate(allMean = mean(stockValue)) -->

<!-- write.csv(df, file = "~/git/ices-dk/rStockOverview/NordicCouncilRefPoints.csv", -->
<!--           row.names = FALSE) -->
<!-- # -->
<!-- ``` -->

<!-- ## Figure 1. ## -->

<!-- F/F~MSY~ and SSB/MSY B~trigger~ averaged by guild for all ecoregions. [Link to .png](https://github.com/ICES-dk/rStockOverview/blob/master/output/NordicCouncilRefPoints_ALL.png) -->

<!-- ```{r echo = FALSE, include = TRUE} -->
<!-- df %>% -->
<!--   ungroup() %>% -->
<!--   distinct(GUILD, METRIC, YEAR) %>% -->
<!--   ggplot(aes(x = YEAR, y = allMean, col = GUILD)) + -->
<!--   geom_line() + -->
<!--   geom_hline(yintercept = 1, col = "grey40", linetype = "dashed") + -->
<!--   # scale_y_continuous(limits = c(0, 3.2)) + -->
<!--   scale_color_manual(values = c("#7fc97f","#ef3b2c","#662506")) + -->
<!--   facet_grid(~METRIC) + -->
<!--   theme_bw() + -->
<!--   theme(legend.position = "bottom", -->
<!--         strip.text = element_text(size = 12, angle = 0, hjust = 0), -->
<!--         strip.background = element_blank(), -->
<!--         legend.key = element_rect(colour = NA)) + -->
<!--   labs(x = "Year", y = "Metric") -->
<!-- ggsave(filename = paste0(plotDir, "NordicCouncilRefPoints_ALL.png"), width = 6.5, -->
<!--        height = 4.5) -->
<!-- ``` -->
<!-- \pagebreak -->

<!-- ## Figure 2. ## -->

<!-- F/F~MSY~ and SSB/MSY B~trigger~ averaged for each ecoregion and guild. [Link to .png](https://github.com/ICES-dk/rStockOverview/blob/master/output/NordicCouncilRefPoints_ecoregion-guild.png) -->

<!-- ```{r echo = FALSE, include = TRUE} -->

<!-- df %>% -->
<!--   mutate(ECOGUILD = paste0(ECOREGION,", ", GUILD)) %>% -->
<!--   ungroup() %>% -->
<!--   # select(ECOGUILD, METRIC, YEAR, ecoGuildMean) %>% -->
<!--   distinct(ECOGUILD, METRIC, YEAR) %>% -->
<!--   filter(YEAR >= 1990) %>% -->
<!--   ggplot(aes(x = YEAR, y = ecoGuildMean, col = METRIC)) + -->
<!--   geom_line() + -->
<!--   geom_hline(yintercept = 1, col = "grey40", linetype = "dashed") + -->
<!--   # scale_y_continuous(limits = c(0, 3.2)) + -->
<!--   facet_grid(GUILD ~ ECOREGION) + -->
<!--   scale_color_manual(values = c("#386cb0","#fdb462")) + -->
<!--   theme_bw() + -->
<!--   theme(legend.position = "bottom", -->
<!--         strip.text = element_text(size = 6, angle = 0, hjust = 0), -->
<!--         axis.text.x = element_text(size = 6, angle = 45), -->
<!--         strip.background = element_blank(), -->
<!--         legend.key = element_rect(colour = NA)) + -->
<!--   labs(x = "Year", y = "Metric") -->
<!-- ggsave(filename = paste0(plotDir, "NordicCouncilRefPoints_ecoregion-guild.png"), width = 6.5, -->
<!--        height = 4.5) -->

<!-- ``` -->
