---
author: ""
date: '`r strftime(Sys.time(), format = "%d %B %Y")`'
output: html_document
params:
  set_title: default
---

---
title: `r paste0("Fishery Overview - ", params$set_title)`
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = paste0("output/", gsub(" ", "_", params$set_title), "/"),
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r catchDatECO, include = FALSE}
catchCountry <- catchDatECO %>%
  group_by(YEAR, Country) %>%
  dplyr::summarize(countryCatch = sum(VALUE)) # %>% # Total annual catch
# Convert country codes to proper names
#
```

```{r figure1, echo = FALSE, include = TRUE}
#
catchPlot <- catchCountry %>%
  group_by(Country) %>%
  dplyr::summarize(countryTotal = sum(countryCatch)) %>% # Overall catch to order plot
  arrange(-countryTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(countryTotal))) %>%
  inner_join(catchCountry, c("Country" = "Country")) %>%
  dplyr::mutate(Country = replace(Country, RANK > 10, "OTHER")) %>%
  group_by(YEAR, Country) %>%
  dplyr::mutate(countryCatch = sum(countryCatch)) %>%
  distinct(YEAR, Country) %>%
  filter(!is.na(YEAR))
#
# Colors
catchPlot$Country <- factor(catchPlot$Country, levels = unique(catchPlot$Country))
myColors <- c(rev(brewer.pal(length(unique(catchPlot$Country)) - 1, "Spectral")), "grey40")
names(myColors) <- levels(catchPlot$Country)
# Order data and limits
catchPlotCast <- dcast(catchPlot, YEAR ~ Country, value.var = "countryCatch")
xval <- as.numeric(catchPlotCast$YEAR)
catchPlotCast <- catchPlotCast[,!(names(catchPlotCast) %in% "YEAR")]
ylim <- c(0, max(rowSums(catchPlotCast, na.rm = T)))
cols <- names(catchPlotCast)
#
# png(filename = paste0(plotDir, "/", id, " Overview_figure1.png"),
#     width = 6.5,
#     height = 4.5,
#     units = "in",
#     res = 600)
#

par(xpd = T,
    mar=c(2.15, 2.25, 0.45, 3.5),
    oma = c(0, 0, 0, 1),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
summary = rep(0, nrow(catchPlotCast))
recent = summary
#
# Create empty plot
plot(c(-100),
     c(-100),
     xlim = range(xval, na.rm = T),
     ylim = ylim,
     ylab = "Landings (tonnes)",
     xlab = "Year")
#
for(c in 1:length(cols)) {
  current = catchPlotCast[[cols[[c]]]]
  summary = summary + current
  polygon(
    x = c(xval, rev(xval)),
    y = c(summary, rev(recent)),
    col = adjustcolor(myColors[[c]], alpha.f = 0.8),
    border = myColors[[c]]
  )
  recent = summary
}
#
legend(x = max(xval) + .25,
       y = max(ylim, na.rm = T),
       legend = rev(cols),
       col = rev(myColors),
       cex = 0.8,
       pch = 15,
       xpd = TRUE,
       bty = "n")
#
# dev.off()
# catchPlot$Country <- factor(catchPlot$Country, levels = rev(unique(catchPlot$Country)))
# myColors <- c("grey40", brewer.pal(length(unique(catchPlot$Country)) - 1, "Spectral"))
# names(myColors) <- levels(catchPlot$Country)
# #
# ggplot(catchPlot, aes(x = YEAR, y = countryCatch)) +
#   geom_area(aes(fill = Country, color = Country), alpha = .8, position = "stack") +
#   scale_fill_manual(values = myColors) +
#   scale_color_manual(values = myColors) +
#   labs(x = "Year",
#        y = "Landings (tonnes)",
#        fill = "Country",
#        color = "Country") +
#   theme_bw()
#   ggsave(filename = paste0(plotDir, id, " Overview_figure1.png"), width = 6.5,
#          height = 4.5, units = "in")

```

Figure 1 corrections  
* Country names and colors should be consistent between Figure 1 and 2. Need to make a look-up table between STECF and ICES country codes
* Merge UK with Scotland (Northern Ireland, Jersey, etc.)  
* Explore 1990- 2006. SL has a plan, but will take some time  
** Not exactly straight-forward to add this info  
* Spain may be missing? Double check  


```{r effortDatECO, include = FALSE}
effortCountry <- effortDatECO %>%
  group_by(YEAR, country) %>%
  dplyr::summarize(countryEffort = sum(VALUE, na.rm = T)) # %>% # Total annual catch
# Convert country codes to proper names

```


```{r figure2, echo = FALSE, include = TRUE}
effortPlot <- effortCountry %>%
  group_by(country) %>%
  dplyr::summarize(countryTotal = sum(countryEffort)) %>% # Overall catch to order plot
  arrange(-countryTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(countryTotal))) %>%
  inner_join(effortCountry, c("country" = "country")) %>%
  dplyr::mutate(country = replace(country, RANK > 10, "OTHER"))%>%
  group_by(YEAR, country) %>%
  dplyr::mutate(countryEffort = sum(countryEffort)) %>%
  distinct(YEAR, country) %>%
  filter(!is.na(YEAR))
#
# effortPlot$country <- factor(effortPlot$country, levels = rev(unique(effortPlot$country)))
# myColors <- c("grey40", brewer.pal(length(unique(effortPlot$country)) - 1, "Spectral"))
# names(myColors) <- levels(effortPlot$country)

# Colors
effortPlot$country <- factor(effortPlot$country, levels = unique(effortPlot$country))
myColors <- c(rev(brewer.pal(length(unique(effortPlot$country)) - 1, "Spectral")), "grey40")
names(myColors) <- levels(effortPlot$country)
# Order data and limits
effortPlotCast <- dcast(effortPlot, YEAR ~ country, value.var = "countryEffort")
xval <- as.numeric(effortPlotCast$YEAR)
effortPlotCast <- effortPlotCast[,!(names(effortPlotCast) %in% "YEAR")]
ylim <- c(0, max(rowSums(effortPlotCast, na.rm = T)))
cols <- names(effortPlotCast)
#
# png(filename = paste0(plotDir, id, " Overview_figure2.png"),
#     width = 6.5,
#     height = 4.5,
#     units = "in",
#     res = 600)
#
par(xpd = T,
    mar=c(2.15, 2.25, 0.45, 3.5),
    oma = c(0, 0, 0, 1),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
summary = rep(0, nrow(effortPlotCast))
recent = summary
#
# Create empty plot
plot(c(-100),
     c(-100),
     xlim = range(xval, na.rm = T),
     ylim = ylim,
     ylab = "Effort (kW days at sea)",
     xlab = "Year")
#
for(c in 1:length(cols)) {
  current = effortPlotCast[[cols[[c]]]]
  summary = summary + current
  polygon(
    x = c(xval, rev(xval)),
    y = c(summary, rev(recent)),
    col = adjustcolor(myColors[[c]], alpha.f = 0.8),
    border = myColors[[c]]
  )
  recent = summary
}
#
legend(x = max(xval) + .25,
       y = max(ylim, na.rm = T),
       legend = rev(cols),
       col = rev(myColors),
       cex = 0.8,
       pch = 15,
       xpd = TRUE,
       bty = "n")
#
# dev.off()
#
# #
# ggplot(effortPlot, aes(x = YEAR, y = countryEffort)) +
#   geom_area(aes(fill = country, color = country), alpha = .8, position = "stack") +
#   scale_fill_manual(values = myColors) +
#   scale_color_manual(values = myColors) +
#   labs(x = "Year",
#        y = "Effort (kW days at sea)",
#        fill = "Country",
#        color = "Country") +
#   theme_bw()
#   ggsave(filename = paste0(plotDir, id, " Overview_figure2.png"), width = 6.5,
#          height = 4.5)
```
Figure 2. Effort (kW days at sea) by nation within the `r params$set_title` ecoregion, as reported to STECF.  

Figure 2 corrections  
* (see figure 1: Country names and colors should be consistent between Figure 1 and 2. Need to make a look-up table between STECF and ICES country codes)  
* [STECF Reference Metadata](https://datacollection.jrc.ec.europa.eu/c/document_library/get_file?uuid=62841ee4-dbbd-4628-a7a7-5036ce5d415b&groupId=10213) claims that 3c == ICES subarea 7a. Double check  
* Check the effort data years... might be an ordinal/nominal issue  

```{r guildDatECO, include = FALSE}
# guildDat <-
#   catchDatECO %>%
#   inner_join(spList, c("Species" = "X3A_CODE")) %>%
#   full_join(fisheryGuild, c("Species" = "newCode"))
#
guildCatch <-
  catchDatECO %>%
  # guildDat %>%
  dplyr::mutate(Fisheries.Guild = ifelse(is.na(Fisheries.Guild), "not defined", Fisheries.Guild)) %>%
  group_by(YEAR, Fisheries.Guild) %>%
  dplyr::summarize(guildCatch = sum(VALUE, na.rm = TRUE)) %>%
  filter(!is.na(YEAR))
#
```

```{r figure3, echo = FALSE, include = TRUE}
guildPlot <- guildCatch %>%
  group_by(Fisheries.Guild) %>%
  dplyr::summarize(guildTotal = sum(guildCatch, na.rm = TRUE)) %>% # Overall catch to order plot
  arrange(-guildTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(guildTotal))) %>%
  inner_join(guildCatch, c("Fisheries.Guild" = "Fisheries.Guild")) %>%
  dplyr::mutate(Fisheries.Guild = replace(Fisheries.Guild, RANK > 10, "OTHER")) %>%
  group_by(YEAR, Fisheries.Guild) %>%
  dplyr::mutate(guildCatch = sum(guildCatch)) %>%
  distinct(YEAR, Fisheries.Guild)
#
# guildPlot$Fisheries.Guild <- factor(guildPlot$Fisheries.Guild, levels = rev(unique(guildPlot$Fisheries.Guild)))
# myColors <- c("grey40", brewer.pal(length(unique(guildPlot$Fisheries.Guild)) - 1, "Spectral"))
# names(myColors) <- levels(guildPlot$Fisheries.Guild)

# Colors
guildPlot$Fisheries.Guild<- factor(guildPlot$Fisheries.Guild, levels = unique(guildPlot$Fisheries.Guild))
myColors <- c(rev(brewer.pal(length(unique(guildPlot$Fisheries.Guild)) - 1, "Spectral")), "grey40")
names(myColors) <- levels(guildPlot$Fisheries.Guild)
# Order data and limits
guildPlotCast <- dcast(guildPlot, YEAR ~ Fisheries.Guild, value.var = "guildCatch")
xval <- as.numeric(guildPlotCast$YEAR)
guildPlotCast <- guildPlotCast[,!(names(guildPlotCast) %in% "YEAR")]
ylim <- c(0, max(rowSums(guildPlotCast, na.rm = T)))
cols <- names(guildPlotCast)
#
# png(filename = paste0(plotDir, id, " Overview_figure3.png"),
#     width = 6.5,
#     height = 4.5,
#     units = "in",
#     res = 600)
#
par(xpd = T,
    mar=c(2.15, 2.25, 0.45, 5.15),
    oma = c(0, 0, 0, 1),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
summary = rep(0, nrow(guildPlotCast))
recent = summary
#
# Create empty plot
plot(c(-100),
     c(-100),
     xlim = range(xval, na.rm = T),
     ylim = ylim,
     ylab = "Landings (tonnes)",
     xlab = "Year")
#
for(c in 1:length(cols)) {
  current = guildPlotCast[[cols[[c]]]]
  summary = summary + current
  polygon(
    x = c(xval, rev(xval)),
    y = c(summary, rev(recent)),
    col = adjustcolor(myColors[[c]], alpha.f = 0.8),
    border = myColors[[c]]
  )
  recent = summary
}
#
legend(x = max(xval) + .25,
       y = max(ylim, na.rm = T),
       legend = rev(cols),
       col = rev(myColors),
       cex = 0.8,
       pch = 15,
       xpd = TRUE,
       bty = "n")
#
# dev.off()

#
# ggplot(guildPlot, aes(x = YEAR, y = guildCatch)) +
#   geom_area(aes(fill = Fisheries.Guild, color = Fisheries.Guild), alpha = .8, position = "stack") +
#   scale_fill_manual(values = myColors) +
#   scale_color_manual(values = myColors) +
#   labs(x = "Year",
#        y = "Landings (tonnes)",
#        fill = "Fishery guild",
#        color = "Fishery guild") +
#   theme_bw()
#   ggsave(filename = paste0(plotDir, id, " Overview_figure3.png"), width = 6.5,
#          height = 4.5)
```
Figure 3. Catch (tonnes) by fishery guild within the `r params$set_title` ecoregion.  

Figure 3 corrections  
* define "not defined" fishery guilds.  


```{r speciesCatch, include = FALSE}
# spDat <-
#   catchDatECO %>%
#   inner_join(spList, c("Species" = "X3A_CODE"))
# #
spCatch <-
  catchDatECO %>%
  dplyr::mutate(English_name = ifelse(is.na(English_name), "not defined", English_name)) %>%
  filter(!is.na(YEAR))

```

```{r  figure4, echo = FALSE, include = TRUE}
#
spPlot <- spCatch %>%
  group_by(Species) %>%
  dplyr::summarize(spTotal = sum(VALUE, na.rm = TRUE)) %>% # Overall catch to order plot
  arrange(-spTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(spTotal))) %>%
  inner_join(spCatch, c("Species" = "Species")) %>%
  dplyr::mutate(Species = replace(Species, RANK > 9, "OTHER"),
                English_name = replace(English_name, RANK > 10, "OTHER")) %>%
  group_by(YEAR, Species, English_name) %>%
  dplyr::mutate(spCatch = sum(VALUE, na.rm = TRUE)) %>%
  distinct(YEAR, Species)

#
# spPlot$English_name <- factor(spPlot$English_name, levels = rev(unique(spPlot$English_name)))
# myColors <- c("grey40", brewer.pal(length(unique(spPlot$English_name)) - 1, "Spectral"))
# names(myColors) <- levels(spPlot$English_name)

# Colors
spPlot$English_name <- factor(spPlot$English_name, levels = unique(spPlot$English_name))
myColors <- c(rev(brewer.pal(length(unique(spPlot$English_name)) - 1, "Spectral")), "grey40")
names(myColors) <- levels(spPlot$English_name)
# Order data and limits
spPlotCast <- dcast(spPlot, YEAR ~ English_name, value.var = "spCatch")
xval <- as.numeric(spPlotCast$YEAR)
spPlotCast <- spPlotCast[,!(names(spPlotCast) %in% "YEAR")]
ylim <- c(0, max(rowSums(spPlotCast, na.rm = T)))
cols <- names(spPlotCast)
#
# png(filename = paste0(plotDir, id, " Overview_figure4.png"),
#     width = 6.5,
#     height = 4.5,
#     units = "in",
#     res = 600)
# #
par(xpd = T,
    mar=c(2.15, 2.25, 0.45, 8),
    oma = c(0, 0, 0, 1),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
summary = rep(0, nrow(spPlotCast))
recent = summary
#
# Create empty plot
plot(c(-100),
     c(-100),
     xlim = range(xval, na.rm = T),
     ylim = ylim,
     ylab = "Landings (tonnes)",
     xlab = "Year")
#
for(c in 1:length(cols)) {
  current = spPlotCast[[cols[[c]]]]
  summary = summary + current
  polygon(
    x = c(xval, rev(xval)),
    y = c(summary, rev(recent)),
    col = adjustcolor(myColors[[c]], alpha.f = 0.8),
    border = myColors[[c]]
  )
  recent = summary
}
#
legend(x = max(xval) + .25,
       y = max(ylim, na.rm = T),
       legend = rev(cols),
       col = rev(myColors),
       cex = 0.8,
       pch = 15,
       xpd = TRUE,
       bty = "n")
#
# dev.off()

#
# ggplot(spPlot, aes(x = YEAR, y = spCatch)) +
#   geom_area(aes(fill = English_name, color = English_name), alpha = .8, position = "stack") +
#   scale_fill_manual(values = myColors) +
#   scale_color_manual(values = myColors) +
#   labs(x = "Year",
#        y = "Landings (tonnes)",
#        fill = "Common name",
#        color = "Common name") +
#   theme_bw()
#   ggsave(filename = paste0(plotDir, id, " Overview_figure4.png"), width = 6.5,
#          height = 4.5)
```
Figure 4. Landings (tonnes) reported to ICES for the 10 species with the greatest gross tonneage within the `r params$set_title`.  

Figure 4 corrections  
* Remove "nei" and "(=Poutassou)" type additions to the FAO species name list  


```{r gearCatch, include = FALSE}
# stecfCatchDat <-
#   stecfCatchDat %>%
#   filter(reg_area %in% ecoAreaEffort) %>%
#   melt(id.vars = c("annex", "reg_area", "country", "reg_gear", "specon", "species"),
#        variable.name = "YEAR",
#        value.name = "VALUE") %>%
#   mutate(METRIC = as.character(gsub(".*\\s", "", YEAR)),
#          YEAR = as.numeric(gsub("\\s.+$", "", YEAR))) %>%
#   filter(METRIC == "L")
#
catchGear <- stecfCatchDatECO %>%
  group_by(YEAR, reg_gear) %>%
  dplyr::summarize(gearCatch = sum(VALUE, na.rm = T)) %>% # Total annual catch
  filter(!is.na(YEAR))
# Convert country codes to proper names
```

```{r figure5, echo = FALSE, include = TRUE}
gearPlot <- catchGear %>%
  group_by(reg_gear) %>%
  dplyr::summarize(gearTotal = sum(gearCatch, na.rm = TRUE)) %>% # Overall catch to order plot
  arrange(-gearTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(gearTotal))) %>%
  inner_join(catchGear, c("reg_gear" = "reg_gear")) %>%
  dplyr::mutate(reg_gear = replace(reg_gear, RANK > 9, "OTHER")) %>%
  group_by(YEAR, reg_gear) %>%
  dplyr::mutate(guildCatch = sum(gearCatch)) %>%
  distinct(YEAR, reg_gear)
#
# gearPlot$reg_gear <- factor(gearPlot$reg_gear, levels = rev(unique(gearPlot$reg_gear)))
# myColors <- c("grey40", brewer.pal(length(unique(gearPlot$reg_gear)) - 1, "Spectral"))
# names(myColors) <- levels(gearPlot$reg_gear)
# Colors
gearPlot$reg_gear <- factor(gearPlot$reg_gear, levels = unique(gearPlot$reg_gear))
myColors <- c(rev(brewer.pal(length(unique(gearPlot$reg_gear)) - 1, "Spectral")), "grey40")
names(myColors) <- levels(gearPlot$reg_gear)
# Order data and limits
gearPlotCast <- dcast(gearPlot, YEAR ~ reg_gear, value.var = "gearCatch")
xval <- as.numeric(gearPlotCast$YEAR)
gearPlotCast <- gearPlotCast[,!(names(gearPlotCast) %in% "YEAR")]
ylim <- c(0, max(rowSums(gearPlotCast, na.rm = T)))
cols <- names(gearPlotCast)
#
# png(filename = paste0(plotDir, id, " Overview_figure5.png"),
#     width = 6.5,
#     height = 4.5,
#     units = "in",
#     res = 600)
# #
par(xpd = T,
    mar=c(2.15, 2.25, 0.45, 7.0),
    oma = c(0, 0, 0, 1),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
summary = rep(0, nrow(gearPlotCast))
recent = summary
#
# Create empty plot
plot(c(-100),
     c(-100),
     xlim = range(xval, na.rm = T),
     ylim = ylim,
     ylab = "Landings (tonnes)",
     xlab = "Year")
#
for(c in 1:length(cols)) {
  current = gearPlotCast[[cols[[c]]]]
  summary = summary + current
  polygon(
    x = c(xval, rev(xval)),
    y = c(summary, rev(recent)),
    col = adjustcolor(myColors[[c]], alpha.f = 0.8),
    border = myColors[[c]]
  )
  recent = summary
}
#
legend(x = max(xval) + .25,
       y = max(ylim, na.rm = T),
       legend = rev(cols),
       col = rev(myColors),
       cex = 0.8,
       pch = 15,
       xpd = TRUE,
       bty = "n")
#
# dev.off()
#
# ggplot(gearPlot, aes(x = YEAR, y = gearCatch)) +
#   geom_area(aes(fill = reg_gear, color = reg_gear), alpha = .8, position = "stack") +
#   scale_fill_manual(values = myColors) +
#   scale_color_manual(values = myColors) +
#   labs(x = "Year",
#        y = "Landings (tonnes)",
#        fill = "Gear type",
#        color = "Gear type") +
#   theme_bw()
#   ggsave(filename = paste0(plotDir, id, " Overview_figure5.png"), width = 6.5,
#          height = 4.5)

```
Figure 5.  EU landings (tonnes) by gear reported to STECF within the `r params$set_title` ecoregion.  

Figure 5 corrections  
* Merge the different gears together  
* Metier overviews  


Table 1. Number of stocks above and below reference points total and divided into fishery guilds  


```{r guildMSY, include = FALSE}
# guildList <- fisheryGuild %>%
#   mutate(speciesID = toupper(gsub( "-.*$", "", Stock.code))) %>%
#   inner_join(speciesID, c("speciesID" = "oldCode")) %>%
#   rename(STOCKID = Stock.code,
#          GUILD = Fisheries.Guild) %>%
#   mutate(STOCKID = tolower(STOCKID),
#          STOCKID = gsub("[[:space:]]", "", STOCKID)) %>%
#   inner_join(stockTable, c("STOCKID" = "STOCKID")) %>%
#   rename(ECOREGION = EcoRegion,
#          YEAR = Year) %>%
#   filter(SpeciesName != "Psetta maxima (historic name)" &
#          ECOREGION == "Baltic Sea") %>%
#   mutate(fishingPressureDescription = gsub("Fishing Pressure: " , "", fishingPressureDescription),
#          fishingPressureDescription = gsub("Fishing pressure: " , "", fishingPressureDescription),
#          stockSizeDescription = ifelse(stockSizeDescription == "NA", "Stock Size: Relative", stockSizeDescription),
#          FmsyDescription = "FMSY",
#          stockSizeDescription = gsub("Stock Size: ", "", stockSizeDescription))
# #
guildMSY <- guildListECO %>%
  group_by(STOCKID) %>%
  mutate(F_FMSY = F / FMSY,
         SSB_MSYBtrigger = SSB / MSYBtrigger) %>%
  melt(id.vars = c("AssessmentYear",  "ECOREGION", "GUILD","STOCKID", "YEAR"),
       measure.vars = c("F_FMSY", "SSB_MSYBtrigger", "F", "FMSY"),
       variable.name = "METRIC",
       value.name = "stockValue") %>%
  filter(!is.na(stockValue)) %>% # remove NA VALUE
  group_by(ECOREGION, GUILD, METRIC, YEAR) %>%
  mutate(ecoGuildMean = mean(stockValue, na.rm = TRUE)) %>%
  group_by(ECOREGION, METRIC, YEAR) %>%
  mutate(ecoValue = mean(stockValue, na.rm = TRUE)) %>%
  group_by(METRIC, GUILD, YEAR) %>%
  mutate(allMean = mean(stockValue, na.rm = TRUE))

#
# guildRatio <- guildMSY %>%
# guildRatio <- guildListECO %>%
#   filter(METRIC %in% c("F_FMSY", "SSB_MSYBtrigger"))
# levels(guildRatio$METRIC) <- c("F/F[MSY]","SSB/MSYB[trigger]", "F", "F[MSY]")

allDat <- guildMSY %>%
  filter(METRIC %in% c("F_FMSY", "SSB_MSYBtrigger")) %>%
  select(pageGroup = GUILD,
         lineGroup = STOCKID,
         YEAR,
         plotGroup = METRIC,
         plotValue = stockValue)
#
oMean <- guildMSY %>%
  filter(METRIC %in% c("F_FMSY", "SSB_MSYBtrigger")) %>%
  distinct(ECOREGION, GUILD, METRIC, YEAR) %>%
  select(pageGroup = GUILD,
         YEAR,
         plotGroup = METRIC,
         plotValue = ecoGuildMean) %>%
  mutate(lineGroup = "MEAN")

allDat <- bind_rows(allDat, oMean)

plotList <- allDat %>%
  group_by(pageGroup) %>%
  select(pageGroup, lineGroup) %>%
  mutate(nLines = n_distinct(lineGroup) - 1,
         COLOR = NA) %>%
  distinct(lineGroup) %>%
  arrange(pageGroup)
#
singleList <- plotList %>%
  filter(nLines == 1) %>%
  mutate(COLOR = colList[1:length(nLines)])
#
normList <- plotList %>%
  filter(nLines <= 9 &
         nLines > 1 &
         lineGroup != "MEAN") %>%
  mutate(COLOR = colList[1:length(nLines)])
#
longList <- plotList %>%
   filter(nLines > 9 &
          lineGroup != "MEAN") %>%
  mutate(COLOR = "grey80")
#
meanList <- plotList %>%
  filter(nLines > 1 &
         lineGroup == "MEAN") %>%
  mutate(COLOR = "grey40")
#
colorList <- bind_rows(singleList, normList, longList, meanList)
allDat <- full_join(colorList, allDat, by = c("pageGroup", "lineGroup"))
#
# allDat <- full_join(plotList, allDat, by = c("pageGroup", "lineGroup"))
#
allDat <-
  allDat %>%
  group_by(pageGroup) %>%
  mutate(nLines = n_distinct(lineGroup)) %>%
  filter(nLines > 2 | lineGroup != "MEAN")
```

```{r figure6, echo = FALSE, include = TRUE}
for(pgGroup in unique(allDat$pageGroup)) { # Data grouped by PaGe (e.g., by ecoregion)
  all.pg <- allDat[allDat$pageGroup == pgGroup,]
  all.pg$plotGroup <- factor(all.pg$plotGroup)
  #
  # plotFileName = paste0(plotDir, id, " Overview_figure6-", pgGroup, ".png")
  # PLOT AVG
  # png(filename = plotFileName,
  #     width = 172.4,
  #     height = 162.6,
  #     units = "mm",
  #     res = 600)
  #
  par(mfrow = c(2,1),
      mar=c(2.15, 2.25, 0.45, 0.25),
      oma = c(0, 0, 1.25, 0),
      usr = c(0,1,0,1),
      mgp=c(3, .35, 0),
      tck=-0.01)
  # Order the lineGroup to make sure mean is plotted
  # if(overallMean == TRUE) {
    if(any(all.pg$lineGroup == "MEAN")) {
      lineGroupOrd <- relevel(factor(unique(all.pg$lineGroup),
                                     ordered = F),
                              ref = "MEAN")
      if(length(lineGroupOrd) > 10) {
        lineGroupOrd <- factor(lineGroupOrd, levels = rev(levels(lineGroupOrd)))
      } # close >= 10
    } #  reorder lineGroupOrd if overallMean == T
    else {
      lineGroupOrd <- factor(unique(all.pg$lineGroup),
                             ordered = T)
    } # reorder lineGroupOrd if overallMean == F
  # } # TRUE overallMean
  # if(overallMean == FALSE ) {
  #   lineGroupOrd <- factor(unique(all.pg$lineGroup),
  #                          ordered = T)
  # } # FALSE overallMean
  #
  for(plGroup in unique(levels(all.pg$plotGroup))) { # Data grouped by PLot (e.g., F or SSB)
    #
    all.pl <- all.pg[all.pg$plotGroup == plGroup,]
    #
    yRange <- c(0, max(all.pl$plotValue, na.rm =T) + max(all.pl$plotValue, na.rm = T) * .15)
    # xRange is the same for both BMSY and FMSY
    xRange <- c(min(all.pg$YEAR[!is.na(all.pg$plotValue)]),
                max(all.pg$YEAR[!is.na(all.pg$plotValue)]))
    #
    plot(NA,
         type = "l",
         ylim = yRange,
         xlim = xRange,
         yaxt = "n",
         xaxt = "n",
         ann = FALSE)
    abline(h = 1.0, lty = 2, col = "black", lwd = 1)
    #
    # Add lines according to the lnGroup
    for(lnGroup in levels(lineGroupOrd)) {
      if(all(is.na(all.pl$plotValue[all.pl$lineGroup == lnGroup]))) {
        lnGroup <- NA
        next
      } # close next if all NA
      if(!all(is.na(all.pl$plotValue[all.pl$lineGroup == lnGroup]))) {
        d <- data.frame(all.pl$plotValue[all.pl$lineGroup == lnGroup],
                        all.pl$YEAR[all.pl$lineGroup == lnGroup])
        d <- d[order(d[,2]),]
        col.d <- as.character(unique(all.pl$COLOR[all.pl$lineGroup == lnGroup]))
        lin.d <- ifelse(lnGroup == "MEAN", 4, 2)
        lines(d[,2], d[,1], col = col.d, lwd = lin.d)
      } # close line plotting
    } # close lnGroup
    #
    # Label axes
    axis(1, at = pretty(xRange), cex.axis = .85)
    mtext("Year", side = 1, line = 1.25, cex= 1)
    axis(2, at = pretty(yRange), cex.axis = .75, las = 1)
    if(plGroup == "F_FMSY") {
      mtext(expression("F/F"["MSY"]), side = 2, line = 1, cex= 1)
    } # close F
    if(plGroup == "SSB_MSYBtrigger") {
      mtext(expression("SSB/MSY B"["trigger"]), side = 2, line = 1, cex= 1)
    } # close SSB
    mtext(pgGroup, side = 3, outer = T, cex= 1.5, font = 2)
    #
    # Legend
    if(length(lineGroupOrd) <= 10) {
      legend("topright",
             legend = as.character(unique(all.pl$lineGroup)),
             fill = as.character(unique(all.pl$COLOR)),
             bty="n",
             ncol = 3,
             cex = .85)
    } # Close less than 9 lines legend
    if(length(lineGroupOrd) > 10) {
      legend("topright",
             legend = "MEAN",
             fill = "grey40",
             bty="n",
             ncol = 1,
             cex = .85)
    } # close more than 10 lines legend
  } # Close plGroup
  # dev.off()
}# Close pgGroup
```


```{r figure6ggplot2, echo = FALSE, include = FALSE}
# guildRatio %>%
#   ungroup() %>%
#   distinct(STOCKID, METRIC, YEAR) %>%
#   ggplot(aes(x = YEAR, y = stockValue, col = STOCKID)) +
#   geom_line(aes(x = YEAR, y = ecoGuildMean), col = "grey30", size = 1.25) +
#   geom_line() +
#   geom_hline(yintercept = 1, col = "grey40", linetype = "dashed") +
#   scale_colour_brewer(palette = "Spectral") +
#   facet_grid(METRIC~GUILD, labeller = label_parsed) +
#   theme_bw() +
#   theme(legend.position = "bottom",
#         strip.text = element_text(size = 12, angle = 0, hjust = 0),
#         strip.background = element_blank(),
#         legend.key = element_rect(colour = NA)) +
#   labs(x = "Year", y = "")
#   ggsave(filename = paste0(plotDir, id, " Overview_figure6.png"), width = 6.5,
#          height = 4.5)
```
Figure 6. Stock trends of F/FMSY and SSB/ MSYBtrigger within the `r params$set_title` ecoregion over time. Full stock names by stock codes are available in Annex Table A.

Figure 6 corrections
* Need to split up into multiple plots (like original)


```{r histGuildMSY, include = FALSE}
FlowFMSY <-
  guildListECO %>%
  group_by(GUILD, YEAR) %>%
  filter(F < FMSY) %>%
  summarize(METRIC = "FlowFMSY",
            VALUE = sum(landings, na.rm = TRUE))
#
FupFMSY <- guildList %>%
  group_by(GUILD, YEAR) %>%
  filter(F > FMSY) %>%
  summarize(METRIC = "FupFMSY",
            VALUE = sum(landings, na.rm = TRUE))
#
noFMSY <- guildList %>%
  group_by(GUILD, YEAR) %>%
  filter(is.na(FMSY)) %>%
  summarize(METRIC = "noFMSY",
            VALUE = sum(landings, na.rm = TRUE))
#
dat <- bind_rows(noFMSY, FupFMSY, FlowFMSY)
cols <- c("FlowFMSY" = "#1B9E77", "FupFMSY" = "#D95F02", "noFMSY" ="#666666")
```


```{r figure7, echo = FALSE, include = TRUE}
ggplot(dat, aes(x = YEAR, y = VALUE)) +
  geom_bar(stat = "identity", aes(fill =factor(METRIC))) +
  theme_bw() +
  scale_fill_manual(values = cols, name = "",
                      labels = c(expression(F < F[MSY]),
                                 expression(F > F[MSY]),
                                 expression(paste(F[MSY], " unk.")))) +
  facet_grid(GUILD ~ ., scales = "free_y") +
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        strip.text = element_text(size = 7, angle = 0, hjust = 0),
        legend.key = element_rect(colour = NA))  +
    labs(x = "Year",
       y = "Landings (tonnes)",
       fill = "Fishery guild")
  # ggsave(filename = paste0(plotDir, id, " Overview_figure7.png"), width = 6.5,
  #        height = 4.5)
```
Figure 7. Total landings removed in relation to FMSY status for stocks within the XX ecoregion over time.  

Figure 7 corrections  

```{r kobe, include = FALSE}
ddt <- guildListECO[guildListECO$YEAR == 2014,
                 # guildList$ECOREGION == "Baltic Sea",
                 colnames(guildListECO) %in% c("STOCKID", "GUILD", "F", "FMSY", "SSB", "MSYBtrigger", "landings", "catches")]
ddt$FMSY[ddt$FMSY == 0] <- NA
ddt$MSYBtrigger[ddt$MSYBtrigger == 0] <- NA
#
ddt$F.FMSY[!is.na(ddt$FMSY)] <- ddt$F[!is.na(ddt$FMSY)] / ddt$FMSY[!is.na(ddt$FMSY)]
ddt$SSB.Btrig[!is.na(ddt$MSYBtrigger)] <- ddt$SSB[!is.na(ddt$MSYBtrigger)] / ddt$MSYBtrigger[!is.na(ddt$MSYBtrigger)]
ddt$landings <- ifelse(is.na(ddt$landings) & !is.na(ddt$catches), ddt$catches, ddt$landings)
#
#determine size of bubbles
ddt$cex <- 10 * sqrt(as.numeric(ddt$landings)/ max(as.numeric(ddt$landings), na.rm=T))
ddt$cex[is.na(ddt$landings)] <- min(ddt$cex, na.rm = T)

ddt$colList <- NA
ddt$colList[ddt$F.FMSY >= 1 &
              ddt$SSB.Btrig >= 1] <- "#D95F02"

ddt$colList[ddt$F.FMSY < 1 &
              ddt$SSB.Btrig >= 1] <- "#1B9E77"

ddt$colList[ddt$F.FMSY > 1 &
              ddt$SSB.Btrig < 1] <- "#D95F02"

ddt$colList[ddt$F.FMSY < 1 &
              ddt$SSB.Btrig < 1] <- "#D95F02"

ddt$textPoints <- (ddt$F.FMSY) + sqrt(ddt$cex)*0.1
```

```{r figure8a, echo = FALSE, include = TRUE}
numRows <- length(unique(ddt$GUILD))

# png(filename = paste0(plotDir, id, " Overview_figure8.png"),
#       width = 172.4 * 2,
#       height = 172.4 * 3,
#       units = "mm",
#       res = 600)

par(mfrow = c(1 + numRows, 2),
    mar = c(2.15, 2.75, 0.45, 2.75),
    oma = c(0, 0, 0, 0),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
par(mfg = c(1, 1))
plot(NA,
     xlim = c(0,5),
     ylim = c(0,5),
     xlab = expression("F / F"[MSY]),
     ylab = expression("SSB / MSY B"[trigger]),
     xaxs = "i",
     yaxs = "i")
# add coloured regions
abline(h = 1, col = "grey60", lty = 2)
abline(v = 1, col = "grey60", lty = 2)
#plot bubbles
points(ddt$F.FMSY, ddt$SSB.Btrig, cex = ddt$cex, pch=21, bg=ddt$colList, col=ddt$colList)
text(ddt$F.FMSY, ddt$SSB.Btrig, ddt$STOCKID, col = "grey30")
#
ddt$colList[is.na(ddt$colList)] <- "grey50"
df <- ddt[order(ddt$landings),]
#
# set up main plot
par(mar = c(2.5, 4.25, 0.45, 2.75),
    oma = c(0, 0, 0, 0),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01,
    new = T)

par(mfg = c(1,2))
barplot(df$landings,
        xlim = c(0, c(max(df$landings) + max(df$landings) * .05)),
        axes = T,
        col = df$colList,
        space = .5,
        border = "grey80",
        horiz = TRUE,
        xlab = "Landings (tonnes)",
        names.arg = df$STOCKID,
        las = 1)
mtexti(text = "all stocks", side = 4, off = .1)
box()

# By type
for(i in 1:length(unique(ddt$GUILD))) {
# png(filename = paste0("~/Fig7_", i, ".png"),
#     width = 172.4 * 2,
#     height = 172.4,
#     units = "mm",
#     res = 600)
GUILD.i <- unique(ddt$GUILD)[i]
# set up main plot
par(mar= c(2.15, 2.75, 0.45, 2.75),
    oma = c(0, 0, 0, 0),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01,
    new = TRUE)
#
par(mfg = c(1 + i, 1))
plot(NA,
     xlim = c(0,5),
     ylim = c(0,5),
     xlab = expression("F / F"[MSY]),
     ylab = expression("SSB / MSY B"[trigger]),
     xaxs = "i",
     yaxs = "i")
# add coloured regions
abline(h = 1, col = "grey60", lty = 2)
abline(v = 1, col = "grey60", lty = 2)
#plot bubbles
ddt.i <- ddt[ddt$GUILD == GUILD.i,]
points(ddt.i$F.FMSY, ddt.i$SSB.Btrig, cex = ddt.i$cex, pch = 21, bg=ddt.i$colList, col=ddt.i$colList)
# text(ddt.i$F.FMSY, ddt.i$SSB.Btrig, ddt.i$STOCKID, col = "grey30")
text(ddt.i$textPoints, ddt.i$SSB.Btrig, ddt.i$STOCKID, col = "grey30")
ddt.i$colList[is.na(ddt.i$colList)] <- "grey50"
df <- ddt.i[order(ddt.i$landings),]

# set up main plot
par(mar= c(2.5, 4.25, 0.45, 2.75),
    oma = c(0, 0, 0, 0),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01,
    new = TRUE)
#
par(mfg = c(1 + i, 2))
barplot(df$landings,
        xlim = c(0, c(max(df$landings) + max(df$landings) * .05)),
        axes = T,
        col = df$colList,
        space = .5,
        border = "grey80",
        horiz = TRUE,
        xlab = "Landings (tonnes)",
        names.arg = df$STOCKID,
        las = 1)
mtexti(text = GUILD.i, side = 4, off = .1)
box()
}
# dev.off()
#
```
Figure 8. Kobe plots and landings of `r params$set_title` stocks by trophic guild (all stocks, pelagic, flatfish, demersal). The left Kobe plots show relative fishing pressure (F/FMSY) and biomass (SSB/ MSY Btrigger) for stocks that have SSB and F relative to reference points (MSY where available, otherwise PA or Qualitative). The size of each bubble corresponds to the ICES official landings in 2014. Stocks in green are exploited below FMSY and have an SSB that is above MSY Btrigger. Stocks in red are exploited above FMSY and have an SSB that is below MSY Btrigger, exploited above FMSY and have an SSB that is above MSY Btrigger, or  and vice versa. Stocks in gray are of unknown status in relation to reference points. Full stock names by stock codes are available in Annex Table A.  

```{r gearEffort, include = FALSE}

effortGear <- effortDatECO %>%
  group_by(YEAR, reg_gear_cod) %>%
  dplyr::summarize(gearEffort = sum(VALUE, na.rm = T)) %>% # Total annual catch
  filter(!is.na(YEAR))
```


```{r figure9, echo = TRUE, include = FALSE}
gearEfPlot <- effortGear %>%
  group_by(reg_gear_cod) %>%
  dplyr::summarize(gearTotal = sum(gearEffort, na.rm = TRUE)) %>% # Overall catch to order plot
  arrange(-gearTotal) %>%
  dplyr::mutate(RANK = min_rank(desc(gearTotal))) %>%
  inner_join(effortGear, c("reg_gear_cod" = "reg_gear_cod")) %>%
  dplyr::mutate(reg_gear_cod = replace(reg_gear_cod, RANK > 10, "OTHER")) %>%
  group_by(YEAR, reg_gear_cod) %>%
  dplyr::mutate(gearEffort = sum(gearEffort)) %>%
  distinct(YEAR, reg_gear_cod)
#
# gearEfPlot$reg_gear_cod <- factor(gearEfPlot$reg_gear_cod, levels = rev(unique(gearEfPlot$reg_gear_cod)))
# myColors <- c("grey40", brewer.pal(length(unique(gearEfPlot$reg_gear_cod)) - 1, "Spectral"))
# names(myColors) <- levels(gearEfPlot$reg_gear_cod)
#
# Colors
gearEfPlot$reg_gear_cod <- factor(gearEfPlot$reg_gear_cod, levels = unique(gearEfPlot$reg_gear_cod))
myColors <- c(rev(brewer.pal(length(unique(gearEfPlot$reg_gear_cod)) - 1, "Spectral")), "grey40")
names(myColors) <- levels(gearEfPlot$reg_gear_cod)
# Order data and limits
gearEfPlotCast <- dcast(gearEfPlot, YEAR ~ reg_gear_cod, value.var = "gearEffort")
xval <- as.numeric(gearEfPlotCast$YEAR)
gearEfPlotCast <- gearEfPlotCast[,!(names(gearEfPlotCast) %in% "YEAR")]
ylim <- c(0, max(rowSums(gearEfPlotCast, na.rm = T)))
cols <- names(gearEfPlotCast)
#
# png(filename = paste0(plotDir, id, " Overview_figure9.png"),
#     width = 6.5,
#     height = 4.5,
#     units = "in",
#     res = 600)
#
par(xpd = T,
    mar=c(2.15, 2.25, 0.45, 7.0),
    oma = c(0, 0, 0, 1),
    mgp = c(1.25, 0.35, 0),
    tck = -0.01)
#
summary = rep(0, nrow(gearEfPlotCast))
recent = summary
#
# Create empty plot
plot(c(-100),
     c(-100),
     xlim = range(xval, na.rm = T),
     ylim = ylim,
     ylab = "Effort (kW days at sea)",
     xlab = "Year")
#
for(c in 1:length(cols)) {
  current = gearEfPlotCast[[cols[[c]]]]
  summary = summary + current
  polygon(
    x = c(xval, rev(xval)),
    y = c(summary, rev(recent)),
    col = adjustcolor(myColors[[c]], alpha.f = 0.8),
    border = myColors[[c]]
  )
  recent = summary
}
#
legend(x = max(xval) + .25,
       y = max(ylim, na.rm = T),
       legend = rev(cols),
       col = rev(myColors),
       cex = 0.8,
       pch = 15,
       xpd = TRUE,
       bty = "n")
#
# dev.off()

# ggplot(gearEfPlot, aes(x = YEAR, y = gearEffort)) +
#   geom_area(aes(fill = reg_gear_cod, color = reg_gear_cod), alpha = .8, position = "stack") +
#   scale_fill_manual(values = myColors) +
#   scale_color_manual(values = myColors) +
#   labs(x = "Year",
#        y = "Effort (Kw Fishing days)",
#        fill = "Gear",
#        color = "Gear") +
#   theme(legend.key = element_rect(colour = NA)) +
#   theme_bw()
#   ggsave(filename = paste0(plotDir, id, " Overview_figure9.png"), width = 6.5,
#          height = 4.5)
```

## Figure 9. Distribution of effort deployed by EU nations by gear type within the Celtic Seas ecoregion over time.    
* No pair trawl  
* Demersal trawl  



## Table 1 will be an annex   
* Add Fpa and Bpa as additional columns.  


For questions, please email <A HREF="mailto:scott.large@ices.dk?subject=Fishery Advice plots">scott.large@ices.dk</A>.  
